---
output: github_document
editor_options: 
  chunk_output_type: console
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
library(tauturri)
library(ggplot2)
library(tidyr)
```
# tauturri

[![Travis build status](https://travis-ci.org/jemus42/tauturri.svg?branch=master)](https://travis-ci.org/jemus42/tauturri)
[![Coverage status](https://codecov.io/gh/jemus42/tauturri/branch/master/graph/badge.svg)](https://codecov.io/github/jemus42/tauturri?branch=master)


The goal of `tauturri` is to get data out of [**Tautulli**](https://github.com/Tautulli/Tautulli) (formerly **PlexPy**) as simply as possible.

The project is in the initial setup phase. Nothing works yet.

## Installation

Do not expect this to make it to CRAN anytime soon.

```r
if (!("remotes" %in% installed.packages())){
  install.packages("remotes")
}

remotes::install_github("jemus42/tauturri")
```
## Setup

In your `~/.Renviron`, set the following:

```
# Tautulli
tautulli_url=<Tautulli URL (with port)>
tautulli_apikey=<Tautilli API key>
```

That's it.  
Alternatively use `Sys.setenv()` to set the appropriate values in a script.

## Server Info

```{r server_info}
info <- get_servers_info()
names(info)
# Probably shouldn't show URL etc.
info[c("name", "version")]
```


## `get_plays_by` [data|dayofweek|...]

All plays in the current year, per day:

```{r get_plays_by_date}
plays <- get_plays_by_date(time_range = lubridate::yday(lubridate::now()))

plays %>% 
  gather(category, playcount, tv, movies, music) %>%
  ggplot(data = ., aes(x = date, y = playcount, fill = category)) +
  geom_col() +
  scale_fill_brewer(palette = "Set1", 
                    labels = c("Movies", "TV", "Music"),
                    breaks = c("movies", "tv", "music")) +
  labs(title = "Plex Plays by Date",
       subtitle = "Showing Movie, TV and Music Categories",
       x = "Date", y = "Plays", fill = "Category") +
  theme_minimal() +
  theme(legend.position = "top")
```


## CoC

Please note that this project is released with a [Contributor Code of Conduct](CODE_OF_CONDUCT.md).  
By participating in this project you agree to abide by its terms.
